THE HERA DISH III : MEASURING ELEMENT CHROMATICITY WITH REFLECTOMETRY.

### 2016-09-15 DishReflectometry/Paper1_v3.tex
Revised section5,6 and added ackknowledgement

\author{
Nipanjana Patra\UCB\myemail,
Aaron~R.~Parsons\UCB,
David~R.~DeBoer\UCB,
Nithyanandan Thyagarajan\ASU,
Aaron  Ewall-Wice\altaffilmark{7},
Gilbert Hsyu\UCB, 
Tsz Kuk Leung\UCB,
James E. Aguirre\altaffilmark{10}, Paul  Alexander\altaffilmark{5}, Zaki S. Ali\altaffilmark{1}, Adam P. Beardsley\altaffilmark{2}, Gianni  Bernardi\altaffilmark{11, 13}, Judd D. Bowman\altaffilmark{2}, Richard F. Bradley\altaffilmark{8}, Chris L. Carilli\altaffilmark{9}, Carina  Cheng\altaffilmark{1}, Cherie~K.~Day\UCB, Eloy  de~Lera~Acedo\altaffilmark{5}, Joshua S. Dillon\altaffilmark{1}, , Gcobisa  Fadana\altaffilmark{13}, Nicolas  Fagnoni\altaffilmark{5}, Randall  Fritz\altaffilmark{13}, Steve R. Furlanetto\altaffilmark{4}, Brian  Glendenning\altaffilmark{9}, Bradley  Greig\altaffilmark{12}, Jasper  Grobbelaar\altaffilmark{13}, Bryna J. Hazelton\altaffilmark{14, 15}, Jacqueline N. Hewitt\altaffilmark{7}, Jack  Hickish\altaffilmark{1}, Daniel C. Jacobs\altaffilmark{2}, Austin  Julius\altaffilmark{13}, MacCalvin  Kariseb\altaffilmark{13}, Saul A. Kohn\altaffilmark{10}, Telalo  Lekalake\altaffilmark{13}, Adrian  Liu\altaffilmark{1, 16}, Anita  Loots\altaffilmark{13}, David  MacMahon\altaffilmark{1}, Lourence  Malan\altaffilmark{13}, Cresshim  Malgas\altaffilmark{13}, Matthys  Maree\altaffilmark{13}, Zachary  Martinot\altaffilmark{10}, Nathan  Mathison\altaffilmark{13}, Eunice  Matsetela\altaffilmark{13}, Andrei  Mesinger\altaffilmark{12}, Miguel F. Morales\altaffilmark{14}, Abraham R. Neben\altaffilmark{7},  Samantha  Pieterse\altaffilmark{13}, Jonathan C. Pober\altaffilmark{3}, Nima  Razavi-Ghods\altaffilmark{5}, Jon  Ringuette\altaffilmark{14}, James  Robnett\altaffilmark{9}, Kathryn  Rosie\altaffilmark{13}, Raddwine  Sell\altaffilmark{13}, Craig  Smith\altaffilmark{13}, Angelo  Syce\altaffilmark{13}, Max  Tegmark\altaffilmark{7}, Peter K.~G. Williams\altaffilmark{6}, Haoxuan  Zheng\altaffilmark{7}
}
%\altaffiltext{2}{To be inserted}}

%\author{ James E. Aguirre\altaffilmark{10}, Paul  Alexander\altaffilmark{5}, Zaki S. Ali\altaffilmark{1}, Adam P. Beardsley\altaffilmark{2}, Gianni  Bernardi\altaffilmark{11, 13}, Judd D. Bowman\altaffilmark{2}, Richard F. Bradley\altaffilmark{8}, Chris L. Carilli\altaffilmark{9}, Carina  Cheng\altaffilmark{1}, Eloy  de~Lera~Acedo\altaffilmark{5}, Joshua S. Dillon\altaffilmark{1}, , Gcobisa  Fadana\altaffilmark{13}, Nicolas  Fagnoni\altaffilmark{5}, Randall  Fritz\altaffilmark{13}, Steve R. Furlanetto\altaffilmark{4}, Brian  Glendenning\altaffilmark{9}, Bradley  Greig\altaffilmark{12}, Jasper  Grobbelaar\altaffilmark{13}, Bryna J. Hazelton\altaffilmark{14, 15}, Jacqueline N. Hewitt\altaffilmark{7}, Jack  Hickish\altaffilmark{1}, Daniel C. Jacobs\altaffilmark{2}, Austin  Julius\altaffilmark{13}, MacCalvin  Kariseb\altaffilmark{13}, Saul A. Kohn\altaffilmark{10}, Telalo  Lekalake\altaffilmark{13}, Adrian  Liu\altaffilmark{1, 16}, Anita  Loots\altaffilmark{13}, David  MacMahon\altaffilmark{1}, Lourence  Malan\altaffilmark{13}, Cresshim  Malgas\altaffilmark{13}, Matthys  Maree\altaffilmark{13}, Zachary  Martinot\altaffilmark{10}, Nathan  Mathison\altaffilmark{13}, Eunice  Matsetela\altaffilmark{13}, Andrei  Mesinger\altaffilmark{12}, Miguel F. Morales\altaffilmark{14}, Abraham R. Neben\altaffilmark{7},  Samantha  Pieterse\altaffilmark{13}, Jonathan C. Pober\altaffilmark{3}, Nima  Razavi-Ghods\altaffilmark{5}, Jon  Ringuette\altaffilmark{14}, James  Robnett\altaffilmark{9}, Kathryn  Rosie\altaffilmark{13}, Raddwine  Sell\altaffilmark{13}, Craig  Smith\altaffilmark{13}, Angelo  Syce\altaffilmark{13}, Max  Tegmark\altaffilmark{7}, Nithyanandan  Thyagarajan\altaffilmark{2}, Peter K.~G. Williams\altaffilmark{6}, Haoxuan  Zheng\altaffilmark{7}}
%\affil{HERA Collaboration}
\altaffiltext{1}{Department of Astronomy, University of California, Berkeley, CA}
\altaffiltext{2}{School of Earth and Space Exploration, Arizona State University, Tempe, AZ}
\altaffiltext{3}{Physics Department, Brown University, Providence, RI}
\altaffiltext{4}{Department of Physics and Astronomy, University of California, Los Angeles, CA}
\altaffiltext{5}{Cavendish Astrophysics, University of Cambridge, Cambridge, UK}
\altaffiltext{6}{Harvard-Smithsonian Center for Astrophysics, Cambridge, MA}
\altaffiltext{7}{Department of Physics, Massachusetts Institute of Technology, Cambridge, MA}
\altaffiltext{8}{National Radio Astronomy Observatory, Charlottesville, VA}
\altaffiltext{9}{National Radio Astronomy Observatory, Socorro, NM}
\altaffiltext{10}{Department of Physics and Astronomy, University of Pennsylvania, Philadelphia, PA}
\altaffiltext{11}{Department of Physics and Electronics, Rhodes University, PO Box 94, Grahamstown, 6140, South Africa}
\altaffiltext{12}{Scuola Normale Superiore, Pisa, Italy}
\altaffiltext{13}{SKA-SA, Cape Town, South Africa}
\altaffiltext{14}{Department of Physics, University of Washington, Seattle, WA}
\altaffiltext{15}{eScience Institute, University of Washington, Seattle, WA}
\altaffiltext{16}{Hubble Fellow}

@@

Reflectometry measurements are carried out at the HERA element prototype in
Green Bank, WV (Figure \ref{fig:heradish}) in order to measure the instrument
response of the feed and dish assembly and characterise the performance.  HERA
element consists off a $14\,m$ diameter parabolic reflector and a
crossed-dipole pair as a feed. The cross dipole antenna pair is identical to
the feed of the PAPER antenna which is suspended at the focal plane of the dish
with the support of three vertical poles. HERA elements are closely spaced with
centre to centre distance between two dishes are equal to the dish diameter.
Therefore, to reduce the coupling between the adjacent dishes, the crossed
dipole feed along with the back plane is encased in a cylindrical cage. The
feed is raised and lowered by a three-pulley system mounted on the three poles.
The focal height of the dish is $5m$.  The detail geometry and electromagnetic
design of of the feed is presented in deBoer et al 2016. \\

@@

%While measuring the return loss of the dish-feed assembly, the signal transmitted by the VNA is reflected first off the feed. This is represented by $\Gamma_{f}$ in equation \ref{eq:power_ratio}. This essentially represents a mismatched impedance between the feed and the 50 Ohm transmission line. In the delay domain, this appears at the zero delay bin. This response is identical whether or not the feed is suspended on the dish. We can, therefore, quantify this response by measuring the feed return loss while the feed is kept on the ground facing the sky. This results in a feed return loss including the surrounding cage structure but excluding the dish response. While a fraction, $\Gamma_{f}$, of the power is reflected off the feed, $1+\Gamma_{f}$ gets transmitted. In the receiving mode, upon initial incidence, $\Gamma_{f}$ of the voltage is reflected back into free space while $1+\Gamma_{f}$ enters the feed, and, in the delay domain, this appears at the zero delay bin. Using the return loss measurement of the feed $(\Gamma_{f})$ and the return loss measurement, $s_{11}$, of the dish, the feed assembly is corrected via equation \ref{eq:power_ratio} for the zero delay component, and the quantity of interest ${I_{rec}\over I_{sky}}$ is estimated. 
%
%
%\begin{figure}[ht]
%\centering
%\includegraphics[width=\linewidth]{plots/delay_spectrum_100_200_BH.png}
%\caption{Delay spectrum of the HERA element, the PAPER element, and the HERA feed estimated by taking the Fourier transform of the measured return loss of power at the feed output. The HERA feed design is driven by the PAPER element with an improved response at all delays. The feed, when suspended on the dish, results in a more complex return loss, and the corresponding delay response is shown in the figure.} %Delay units are incorrect!!!! Should be ns not GHz!!!!
%\label{fig:delay_spectrum}
%\end{figure}
\subsection{Delay spectrum of sub bands}

The dominant term in the expression of  return loss of the HERA element in
receiving mode (\ref{eq11}) is the zero delay term $(1+\Gamma_{f})$. As
mentioned earlier, the feed reflection coefficient $\Gamma_{a}$ shows two
resonances in between 100-140~MHz and 160-200~MHz. While the one at high
frequency is a wider peak, the low frequency resonance shows a sharp feature in
frequency. This dominates the overall shape of the delay spectrum in figure
\ref{ds_feed_on_dish_trans}.\\ Also, In HERA analysis, the 21~cm power spectrum
is estimated by gridding the observed data along the line of sight distance i.e
is in frequency or redshift and spatial frequency scale
$k$~\citep{liu_et_al2014a}. At particular redshift, the bandwidth of
observation is so chosen that over the corresponding $\Delta z$, the 21~cm
signal does not significantly evolve. Typically, the the 21~cm brightness
temperature fluctuation evolve over redshift scale $\Delta
z>0.5$~\citep{loeb_zaldarriaga2004},~\citep{lidz_et_al2008}. Hence, the delay
spectrum is estimated over smaller bandwidths.\\ We estimate the instrument
delay spectrum over various sub bands between 100 to 200~MHz as shown in figure
\ref{ds_full_sub_band}. Each panel of figure \ref{ds_full_sub_band} shows the
delay spectrum estimated from the returnloss measurement of the HERA element
between 100-200, 100-140, 140-160, 160 to 200~MHz respectively. Each panel also
compares the estimated delay spectrum with two simulated delay spectra. The
blue curve is the delay spectrum estimated from the simulated return loss of
the feed and the feed-dish assembly that is shown in figure
\ref{ds_feed_on_dish_trans}. Sub band delay spectra are wider compared to full
band delay spectrum.  Shape of the resonant peaks determines the roll of rate
of the delay spectrum in the range of 100-140~MHz and 160~200MHz. At higher
frequency, our measurements closely follows the em simulations except around
120~ns where the cable reflection between the antenna and the backend manifests
itself at all frequencies. \\ The shaded region of each panel shows the EoR to
foreground power ratio required for detection of 21~cm power spectrum at those
individual delays~\citep{Thyagarajan_et_al2016}. This ratio is computed by
using the HFSS simulation of chromatic antenna beam as well as return loss
(figure \ref{RL_mag_dish}) and the sky models. Diffused sky foreground model is
incorporated from~\citep{deolivieracosta_et_al2008} whereas the point source
contribution is estimated by combining the NRAO VLA Sky Survey (NVSS) at
1.42~GHz~\citep{Condon_1998}, Sydney University Molonglo sky Survey (SUMSS)
~\citep{Bock_et_al_1999}, \citep{Mauch_et_al_2003} at 843~MHz. The EoR signal
is simulated by using 21cmFAST \citep{Messinger_et_al2011}. The model
parameters used by~\cite{Thyagarajan_et_al2016} for the EoR signal simulation
are : Virial temperature of minimum mass of dark matter halos that host
ionizing sources, $T_{vir}^{min} = 2*10^4 K$, Ionising efficiency $\eta = 20$,
Mean Free Path of UV photons $R_{mfp} = 15Mpc.$ For these model parameter
values, the redshift of $50\%$ reionization is predicted to be at $z = 8.5$ at
150MHz.  Ideally, the delay response of the smooth foreground is confined at
lower delays whereas the same for the EoR signal is spread across the entire
delay range. However, due to system chromaticity of the simulated response of
the HERA element, foreground spills over the higher delays.
~\cite{Thyagarajan_et_al2016} computes the required attenuation of the
foreground with respect to the EoR power available at that delay in order for a
detection of the EoR signal at that delay mode. It is shown that for a given
delay mode, the estimate of a lower $k_{\parallel}$ mode requires a higher
attenuation compared to a higher $k_{\parallel}$ mode. (For details
~\cite{Thyagarajan_et_al2016}).

\begin{figure*}[ht]
\begin{minipage}[b]{0.5\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/100_200.png}
\end{minipage}
\hspace{0.1cm}
\begin{minipage}[b]{0.5\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/100_140.png}
\end{minipage}
\vspace{0.1cm}
\begin{minipage}[b]{0.5\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/140_160.png}
\end{minipage}
\hspace{0.1cm}
\begin{minipage}[b]{0.5\linewidth}
\centering
\includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/160_200.png}
\end{minipage}
\caption{Magnitude and phase of the return loss of the feed as simulated and measured. While both the measurement and the simulation shows similar resonance around $120~MHz$, the simulation shows a better matching to a 50 Ohm transmission line compared to the measurements. The measurement also has some small scale fluctuation due to multiple reflection of the signal at the VNA input. }   
\label{ds_full_sub_band}
\end{figure*}

\section{\textbf{Effect of instrument delay spectrum on 21cm power spectrum measurements}}

21cm power spectrum measurements are limited by challenges posed by the low
frequency radio foreground that is order of magnitude brighter than the
expected power spectrum amplitude. While PAPER has established the till date
the most stringent upper limit on the 21cm power spectrum measurement, the need
for increased sensitivity called for increased collecting area per PAPER
element. This has driven to the parabolic reflector antenna based design of the
PAPER successor HERA where essentially the PAPER antenna with minor
modification of the ground plane-side plane assembly works as the feed and thus
having larger collecting area per element. Additional limitations on PAPER and
its contemporaries are imposed by the spectral structure of the system
response. Sky signal is frequency modulated by the system bandpass response. In
delay spectrum technique of 21cm power spectrum estimation, sky signal is
convolved with the system response in the delay domain. In this process of
convolution, the frequency dependent system response with rapid frequency
variation results in spreading of the smooth spectrum foreground of the sky
signal to the delays in which EoR power spectrum is to be estimated. This
essentially limits the capacity of any experiment to probe the smaller spatial
scales of fluctuations. \\ Figure \ref{fig:sim_em} and \ref{fig:sim_pk} shows
the measurement presented this paper in comparison with the simulations.
Simulations and measurements are in good agreement with each other up to around
$60~ns$ up to which the structures in the delay domain are mostly caused due to
signal reflections in the feed structure. Since the simulated return loss shows
a better match of the antenna to the 50 Ohm transmission line. At zero delay ,
in case of simulation, almost $100\%$ of the sky signal is received whereas in
case of measurements, this match is found to be less than $5~dB$ resulting in
partial coupling of the sky signal to the system. Given all the reflections
unaltered, if the matching in between the feed and the transmission line is
improved by about $10~dB$, which is achievable in reality, the delay spectrum
would improve substantially. This is plotted in grey. The work is currently
under progress to improve the feed return loss at least by  $10dB$ (Eloy et al
2016 in prep?). Beyond $60~nS$ other multiple reflections manifests themselves
at higher delays and the delay spectrum of the measurement and simulations
begin to deviate from each other.\\ Thyagarajan et al 2016) has presented the
detailed sensitivity calculations of HERA is using a comprehensive foreground
model as well as model for EoR power spectrum for various simulated antenna
element response. The sensitivity is quantified as a ratio of EoR signal power
to the foreground power at various $\bold k_{\parallel}$ mode i.e at various
delays. The theoretical limits for the level of foreground attenuation required
relative to the EoR signal in order to reduce the foreground contaminations at
the delay modes significant for power spectrum measurements are shown for three
different lower limits of $k_\parallel$ values.  The response is computed for
the redshift of $z=8.47$ at frequency $150~MHz$ over a bandwidth of $10~MHz$.
This simulation shows the effect of chromatic antenna response and how that
contaminates the delay modes beyond the horizon limit. Thus, this establishes a
very stringent limits of required foreground attenuation relative to EoR signal
which demands almost an ideal system performance. \\

%As shown in section (), multiple reflection in the antenna system generates multiple copies of the sky signal and thus results in additional foreground contaminations in the delay modes where EOR power spectrum is measurable in case of no reflections. Reflectometry measurements shows the relative strength with which the multiple copies of the signal shows up at various delays.

\begin{figure}
\centering
\includegraphics[width=\linewidth]{GB_reflectometry_part3/plot/simulation_comparison.png}
\caption{Delay spectrum of HERA element estimated from the reflectometry measurements by a vector network analyser compared to the limits of foreground simulation (Thyagarajan et al).}
\label{fig:sim_fg_Nithya}
\end{figure}

The HERA analysis pipeline for power spectrum estimation exploits the inverse covariance weighting technique to reduce the foreground contribution to the measured visibility data. In the light of this analysis technique we further investigate the limits of required instrumental delay response from what is established by foreground simulation in Thyagarajan et al 2016. In the following section we briefly describe the power spectrum estimation technique used in HERA analysis and the inverse covariance weighting. In the next section we evaluate the estimated instrument delay response performance in the context of covariance weighting.

\subsection{Power spectrum estimation:}

HERA power spectrum estimation is done using the Optimal Quadratic Estimator
(OQE) formalism that has been outlined in extensive detail in (Liu and Tegmark
2011), (Dillon et al 2013), (Liu et al 2014a,2014b), (Trott et al 2016), (Ali
et al 2015). We briefly  describe the OQE formalism here.\\ HERA instrument
aims at measuring the redshifted 21~cm power spectrum
$P_{21}(k_\perp,k_\parallel)$, conventionally written as,

>>>>

    \author{
    Nipanjana Patra\UCB\myemail,
    Aaron~R.~Parsons\UCB,
    David~R.~DeBoer\UCB,
    Nithyanandan Thyagarajan\ASU,
    Aaron  Ewall-Wice\altaffilmark{7},
    Gilbert Hsyu\UCB, 
    Tsz Kuk Leung\UCB,
    James E. Aguirre\altaffilmark{10}, Paul  Alexander\altaffilmark{5}, Zaki S. Ali\altaffilmark{1}, Adam P. Beardsley\altaffilmark{2}, Gianni  Bernardi\altaffilmark{11, 13}, Judd D. Bowman\altaffilmark{2}, Richard F. Bradley\altaffilmark{8}, Chris L. Carilli\altaffilmark{9}, Carina  Cheng\altaffilmark{1}, Cherie~K.~Day\UCB, Eloy  de~Lera~Acedo\altaffilmark{5}, Joshua S. Dillon\altaffilmark{1}, , Gcobisa  Fadana\altaffilmark{13}, Nicolas  Fagnoni\altaffilmark{5}, Randall  Fritz\altaffilmark{13}, Steve R. Furlanetto\altaffilmark{4}, Brian  Glendenning\altaffilmark{9}, Bradley  Greig\altaffilmark{12}, Jasper  Grobbelaar\altaffilmark{13}, Bryna J. Hazelton\altaffilmark{14, 15}, Jacqueline N. Hewitt\altaffilmark{7}, Jack  Hickish\altaffilmark{1}, Daniel C. Jacobs\altaffilmark{2}, Austin  Julius\altaffilmark{13}, MacCalvin  Kariseb\altaffilmark{13}, Saul A. Kohn\altaffilmark{10}, Anna Lebedeva\UCB, Telalo  Lekalake\altaffilmark{13}, Adrian  Liu\altaffilmark{1, 16}, Anita  Loots\altaffilmark{13}, David  MacMahon\altaffilmark{1}, Lourence  Malan\altaffilmark{13}, Cresshim  Malgas\altaffilmark{13}, Matthys  Maree\altaffilmark{13}, Zachary  Martinot\altaffilmark{10}, Nathan  Mathison\altaffilmark{13}, Eunice  Matsetela\altaffilmark{13}, Andrei  Mesinger\altaffilmark{12}, Miguel F. Morales\altaffilmark{14}, Abraham R. Neben\altaffilmark{7},  Samantha  Pieterse\altaffilmark{13}, Jonathan C. Pober\altaffilmark{3}, Nima  Razavi-Ghods\altaffilmark{5}, Jon  Ringuette\altaffilmark{14}, James  Robnett\altaffilmark{9}, Kathryn  Rosie\altaffilmark{13}, Raddwine  Sell\altaffilmark{13}, Craig  Smith\altaffilmark{13}, Angelo  Syce\altaffilmark{13}, Max  Tegmark\altaffilmark{7}, Peter K.~G. Williams\altaffilmark{6}, Haoxuan  Zheng\altaffilmark{7}
    }

    \altaffiltext{1}{Department of Astronomy, University of California, Berkeley, CA}
    \altaffiltext{2}{School of Earth and Space Exploration, Arizona State University, Tempe, AZ}
    \altaffiltext{3}{Physics Department, Brown University, Providence, RI}
    \altaffiltext{4}{Department of Physics and Astronomy, University of California, Los Angeles, CA}
    \altaffiltext{5}{Cavendish Astrophysics, University of Cambridge, Cambridge, UK}
    \altaffiltext{6}{Harvard-Smithsonian Center for Astrophysics, Cambridge, MA}
    \altaffiltext{7}{Department of Physics, Massachusetts Institute of Technology, Cambridge, MA}
    \altaffiltext{8}{National Radio Astronomy Observatory, Charlottesville, VA}
    \altaffiltext{9}{National Radio Astronomy Observatory, Socorro, NM}
    \altaffiltext{10}{Department of Physics and Astronomy, University of Pennsylvania, Philadelphia, PA}
    \altaffiltext{11}{Department of Physics and Electronics, Rhodes University, PO Box 94, Grahamstown, 6140, South Africa}
    \altaffiltext{12}{Scuola Normale Superiore, Pisa, Italy}
    \altaffiltext{13}{SKA-SA, Cape Town, South Africa}
    \altaffiltext{14}{Department of Physics, University of Washington, Seattle, WA}
    \altaffiltext{15}{eScience Institute, University of Washington, Seattle, WA}
    \altaffiltext{16}{Hubble Fellow}

@@

    Reflectometry is a method of determining the multiple reflection of any signal within a system. 
    If applied to a radio telescope such as a parabolic dish, this could determine the extent to which 
    sky signal is reflected back and forth between the reflector and the feed ~\citep{2015arXiv150205862P}.
    Reflectometry measurements are carried out at the HERA element prototype in
    Green Bank, WV (Figure \ref{fig:heradish}) in order to measure the instrument
    response of the feed and dish assembly and characterise the performance.  HERA
    element consists off a $14\,m$ diameter parabolic reflector and a
    crossed-dipole pair as a feed. The cross dipole antenna pair is identical to
    the feed of the PAPER antenna which is suspended at the focal plane of the dish
    with the support of three vertical poles. HERA elements are closely spaced with
    centre to centre distance between two dishes are equal to the dish diameter.
    Therefore, to reduce the coupling between the adjacent dishes, the crossed
    dipole feed along with the back plane is encased in a cylindrical cage. The
    feed is raised and lowered by a three-pulley system mounted on the three poles.
    The focal height of the dish is $5m$.  The detail geometry and electromagnetic
    design of of the feed is presented in deBoer et al 2016. \\

@@

    %While measuring the return loss of the dish-feed assembly, the signal transmitted by the VNA is reflected first off the feed. This is represented by $\Gamma_{f}$ in equation \ref{eq:power_ratio}. This essentially represents a mismatched impedance between the feed and the 50 Ohm transmission line. In the delay domain, this appears at the zero delay bin. This response is identical whether or not the feed is suspended on the dish. We can, therefore, quantify this response by measuring the feed return loss while the feed is kept on the ground facing the sky. This results in a feed return loss including the surrounding cage structure but excluding the dish response. While a fraction, $\Gamma_{f}$, of the power is reflected off the feed, $1+\Gamma_{f}$ gets transmitted. In the receiving mode, upon initial incidence, $\Gamma_{f}$ of the voltage is reflected back into free space while $1+\Gamma_{f}$ enters the feed, and, in the delay domain, this appears at the zero delay bin. Using the return loss measurement of the feed $(\Gamma_{f})$ and the return loss measurement, $s_{11}$, of the dish, the feed assembly is corrected via equation \ref{eq:power_ratio} for the zero delay component, and the quantity of interest ${I_{rec}\over I_{sky}}$ is estimated. 
    %
    %
    %\begin{figure}[ht]
    %\centering
    %\includegraphics[width=\linewidth]{plots/delay_spectrum_100_200_BH.png}
    %\caption{Delay spectrum of the HERA element, the PAPER element, and the HERA feed estimated by taking the Fourier transform of the measured return loss of power at the feed output. The HERA feed design is driven by the PAPER element with an improved response at all delays. The feed, when suspended on the dish, results in a more complex return loss, and the corresponding delay response is shown in the figure.} %Delay units are incorrect!!!! Should be ns not GHz!!!!
    %\label{fig:delay_spectrum}
    %\end{figure}

  \subsection{Comparison with simulations:}
  \begin{figure}{H}
  \centering
  \includegraphics[width=\linewidth]{GB_reflectometry_part3/plot/simulation_comparison2.png}
  \caption{Delay spectrum of HERA element estimated from the reflectometry measurements by a vector network analyser compared to the limits of foreground simulation (Thyagarajan et al).}
   \label{fig:sim_em}
   \end{figure}
 \subsubsection{Electromagnetic simulation:}  
We compare the delay spectrum estimated from our measurements with the same derived from the return loss obtained from the HFSS simulations of the HERA element (figure \ref{fig:sim_em}). The simulation is in good agreement with the measurements up to about 80~ns after which the cable reflection starts to manifests. The dominant term in the expression of  return loss of the HERA element in
    receiving mode (equation \ref{eq11}) is the zero delay term $(1+\Gamma_{f})$. As
    mentioned earlier, the feed reflection coefficient $\Gamma_{a}$ shows two
    resonances in between 100-140~MHz and 160-200~MHz. While the one at high
    frequency is a wider peak, the low frequency resonance shows a sharp feature in
    frequency. This dominates the overall shape of the delay spectrum in figure
    \ref{fig:sim_em}.\\
  \subsubsection{Time domain simulation:}  
    We also compare our measurements with the time domain simulation presented in ~\cite{Ewall-Wice_et_al2016}. In this simulation, electromagnetic response of the HERA element is determined as a function of time using the commercial numerical simulation software Microwave Studio developed by Computer Simulation Technology. The simulation assumed a constant $125\Omega$ impedance at the dipole terminals. In reality, dipole impedance is function of frequency across the entire band. This results in deviation between the simulated delay response and the delay spectrum estimate of our measurements. \\
     \subsubsection{Foreground simulation:}  
    We also compare our measurement with the foreground simulation of~\citep{Thyagarajan_et_al2016} as shown in the first panel of figure \ref{ds_full_sub_band}. The shaded region of each panel shows the EoR to
    foreground power ratio required for detection of 21~cm power spectrum at those
    individual delays~\citep{Thyagarajan_et_al2016}. This ratio is computed by
    using the HFSS simulation of chromatic antenna beam and the sky models. Diffused sky foreground model is
    incorporated from~\citep{deolivieracosta_et_al2008} whereas the point source
    contribution is estimated by combining the NRAO VLA Sky Survey (NVSS) at
    1.42~GHz~\citep{Condon_1998}, Sydney University Molonglo sky Survey (SUMSS)
    ~\citep{Bock_et_al_1999}, \citep{Mauch_et_al_2003} at 843~MHz. The EoR signal
    is simulated by using 21cmFAST \citep{Messinger_et_al2011}. The model
    parameters used by~\cite{Thyagarajan_et_al2016} for the EoR signal simulation
    are : Virial temperature of minimum mass of dark matter halos that host
    ionizing sources, $T_{vir}^{min} = 2*10^4 K$, Ionising efficiency $\eta = 20$,
    Mean Free Path of UV photons $R_{mfp} = 15Mpc.$ For these model parameter
    values, the redshift of $50\%$ reionization is predicted to be at $z = 8.5$ at
    150MHz.  Ideally, the delay response of the smooth foreground is confined at
    lower delays whereas the same for the EoR signal is spread across the entire
    delay range. However, due to system chromaticity of the simulated response of
    the HERA element, foreground spills over the higher delays.
    ~\cite{Thyagarajan_et_al2016} computes the required attenuation of the
    foreground with respect to the EoR power available at that delay in order for a
    detection of the EoR signal at that delay mode. It is shown that for a given
    delay mode, the estimate of a lower $k_{\parallel}$ mode requires a higher
    attenuation compared to a higher $k_{\parallel}$ mode. (For details
    ~\cite{Thyagarajan_et_al2016}). \\
     This simulation also, however, does not incorporate the frequency dependent antenna impedance that 
     results in a frequency dependent return loss of power at the antenna terminal. Hence, the shaded region shows the most      
     stringent limits of  EoR to foreground power ratio and sets the upper most limit of the required system performance under the assumption of non-chromatic return loss.

    \subsubsection{Delay spectrum of sub bands}
    In HERA analysis, the 21~cm power spectrum
    is estimated by gridding the observed data along the line of sight distance i.e
    is in frequency or redshift and spatial frequency scale
    $k$~\citep{liu_et_al2014a}. At particular redshift, the bandwidth of
    observation is so chosen that over corresponding $\Delta z$, the 21~cm
    signal does not significantly evolve. Typically, the the 21~cm brightness
    temperature fluctuation evolve over redshift scale $\Delta
    z>0.5$~\citep{loeb_zaldarriaga2004},~\citep{lidz_et_al2008}. Hence, the delay
    spectrum is estimated over smaller bandwidths.\\ We estimate the instrument
    delay spectrum over various sub bands between 100 to 200~MHz as shown in figure
    \ref{ds_full_sub_band}. Each panel of figure \ref{ds_full_sub_band} shows the
    delay spectrum estimated from the return loss measurement of the HERA element
    between 100-200, 100-140, 130-170, 160 to 200~MHz respectively. Each panel also
    compares the estimated delay spectrum with em simulation of~\cite{deBoer_2016} at various subband.  Sub band delay spectra are wider compared to full
    band delay spectrum.  Shape of the resonant peaks determines the roll off rate
    of the delay spectrum at all frequency ranges. At higher
    frequency, our measurement closely follows the em simulations except around
    80-120~ns where the cable reflection between the antenna and the backend manifests
    itself at all frequencies. \\ 
    The shaded regions are however represents the EoR to Foreground power ratio simulated across the entire band.
    The HFSS simulation of chromatic antenna beam, as incorporated by \cite{Thyagarajan_et_al2016} varies smoothly  	across frequency resulting in no significant changes in this simulation at various sub bands.  
     HERA system performance conforms directly to the limits as posed by simulations, at frequencies $>160~MHz$. With the measured system response including the multiple reflections, the instrument would be able to probe the spatial modes of interest $k_{\parallel}>0.2$ with very little foreground bleeding $k_{\parallel} \approx 0.2$.
      At other frequencies, it is possible to do a successful measurement by weighting down the
      foreground contribution in the measured data. This is discussed in the following section.
    \begin{figure*}[ht]
    \begin{minipage}[b]{0.5\linewidth}
    \centering
    \includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/100_200.png}
    \end{minipage}
    \hspace{0.1cm}
    \begin{minipage}[b]{0.5\linewidth}
    \centering
    \includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/100_140.png}
    \end{minipage}
    \vspace{0.1cm}
    \begin{minipage}[b]{0.5\linewidth}
    \centering
    \includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/130_170.png}
    \end{minipage}
    \hspace{0.1cm}
    \begin{minipage}[b]{0.5\linewidth}
    \centering
    \includegraphics[angle=0, width=\linewidth]{GB_reflectometry_part3/plot/160_200.png}
    \end{minipage}
    \caption{Magnitude and phase of the return loss of the feed as simulated and measured. While both the measurement and the simulation shows similar resonance around $120~MHz$, the simulation shows a better matching to a 50 Ohm transmission line compared to the measurements. The measurement also has some small scale fluctuation due to multiple reflection of the signal at the VNA input. }   
    \label{ds_full_sub_band}
    \end{figure*}
 The HERA analysis pipeline for power spectrum estimation exploits the inverse covariance weighting to reduce the foreground contribution to the measured visibility data. In the light of this analysis technique we further investigate the limits of EoR to foreground power ratio from what is established by foreground simulation in \cite{Thyagarajan_et_al2016}. In the following section we briefly describe the power spectrum estimation technique used in HERA analysis and the inverse covariance weighting. We evaluate the instrument delay response in the context of covariance weighting.

    \section{\textbf{Power spectrum estimation}}

    HERA power spectrum estimation is done using the Optimal Quadratic Estimator
    (OQE) formalism that has been outlined in extensive detail in  ~\cite{liu_et_al2010}, ~\cite{dillon_et_al2013a}, ~\cite{liu_et_al2014a}, ~\cite{liu_et_al2014b}, ~\cite{trott_et_al2012}, ~\cite{Ali_et_al2015}. We briefly  describe the OQE formalism here.
    Conventionally, the 21~cm power spectrum $P_{21}(k_\perp,k_\parallel)$ is written as,
